---
title: "Covid-19"
author: "Manikanta"
date: "2024-03-24"
output: html_document
---

````{r setup, include=FALSE}
library(flexdashboard)
library(plotly)

# Your data (replace with your actual data)
data <- read.csv(file.choose())
```
## R Markdown
```{r data}
summary(data)
```

## Including Plots

#-> Chart 1: Analyze the distribution of COVID-19 confirmed cases among different countries to identify high-impact regions and inform resource allocation decisions.

```{r pressure, echo=FALSE}
plot_ly(data, labels = ~Country, values = ~Confirmed, type = 'pie', textposition = 'inside', textinfo = 'label+percent') %>%
  layout(title = 'COVID-19 Confirmed Cases by Country')

```


#-> Chart 2:  Visualize and compare the distribution of confirmed, deaths, recovered, and active COVID-19 cases across different countries using a stacked bar chart to understand the pandemic's impact globally.
```{r}
plot_ly(data, x = ~Country, y = ~Confirmed, type = 'bar', name = 'Confirmed') %>%
  add_trace(y = ~Deaths, name = 'Deaths') %>%
  add_trace(y = ~Recovered, name = 'Recovered') %>%
  add_trace(y = ~Active, name = 'Active') %>%
  layout(title = 'Stacked Bar Chart',
         xaxis = list(title = 'Country'),
         yaxis = list(title = 'Count'),
         barmode = 'stack')


```

#-> Chart 3:  Illustrate the proportion of confirmed cases and deaths across countries while comparing their distribution using a pie chart to understand the severity of the COVID-19 pandemic.

```{r}
plot_ly(data, labels = ~Country, values = ~Confirmed, type = "pie", name = "Confirmed") %>%
  add_trace(values = ~Deaths, name = "Deaths") %>%
  layout(title = "Confirmed Deaths vs Active",
         showlegend = TRUE)

```



#-> Chart 4:Visualize the comparison between confirmed cases and deaths across different countries using a grouped bar chart to gain insights into the impact of COVID-19 on various regions.

```{r}
plot_ly(data, x = ~Country, y = ~Confirmed, type = 'bar', name = 'Confirmed') %>%
  add_trace(y = ~Deaths, name = 'Deaths') %>%
  layout(title = 'Bar Chart Comparison',
         xaxis = list(title = 'Country'),
         yaxis = list(title = 'Count'),
         barmode = 'group')

```


#-> Chart 5:  Explore the distribution of deaths per 100 COVID-19 cases across regions to understand the severity and variability of fatality rates.

```{r}
ggplot(data, aes(x = Deaths100Cases)) +
  geom_histogram(binwidth = 5, fill = "skyblue", color = "black") +
  labs(title = "Distribution of Deaths per 100 Cases",
       x = "Deaths per 100 Cases",
       y = "Frequency") +
  theme_minimal()

```